Illusion Game Validation (Study 2)

### 2022-08-16 manuscript.Rmd
script

<!-- Intro  & Gaps-->
Visual illusions are blabla. Despite the historical interest, several gaps remained unanswered:

This could be caused by the relative difficulty to adapt visual illusions to an experimental setting, which typically requires the parametric modulation of variables at stake.

<!-- Target, strength, difficulty -->
Many visual illusions can be seen as made of *targets* (e.g., parallel lines, same-size circles, same-length lines), which perception is biased by the *context* (e.g., parallel lines are seen as angled, circle or segments appear of different lengths). To date, most of the paradigms prompt the subjective extent the context biases the perception ("how much does the circle appear bigger", e.g., **REFS**).

Although visual illusions are inherently tied to subjective perception, we tested a reversal of the traditional paradigm to access the "objective" effect of illusions.

To achieve this, we first developed a parametric framework to generate visual illusions that we implemented and made accessible in the open-source Pyllusion software (REF). This allows us to generate stimuli ...

In the present study, we will test this novel paradigm to ...

>>>>

<!-- Intro  & Gaps-->
Visual illusions are *blabla*. Despite the historical interest, several gaps remained unanswered: *blabla*. One key challenge hindering the further development of the field is the relative difficulty to adapt visual illusions to an experimental setting, which typically requires the controlled modulation of the specific variables of interest.

<!-- Pyllusion -->
To address this issue, we first developed a parametric framework to generate visual illusions, that we implemented and made accessible in the open-source *Pyllusion* software (REF).

<!-- Target, strength, difficulty -->
Many visual illusions can be seen as made of *targets* (e.g., parallel lines, same-size circles, same-length lines), which perception is biased by the *context* (e.g., parallel lines are seen as angled, circle or segments appear of different lengths).

This framework allows the continuous and independent modulation of *illusion strength* and *task difficulty*.

To date, most of the paradigms prompt the subjective extent the context biases the perception ("how much does the circle appear bigger", e.g., **REFS**).

Although visual illusions are inherently tied to subjective perception, we tested a reversal of the traditional paradigm to access the "objective" effect of illusions. By generating stimuli that

In the present set of studies, we will test this novel paradigm to investigate 1) if the effect of illusion can be manipulated continuously, 2) whether 10 different illusions share a common latent factor, 3) how the the inter-individual sensitivity to illusions relates to other characteristics, such as sex or personality.

## Methods

### 2022-08-16 study2/study2.Rmd
script

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "meanfield",
  brms.backend = "cmdstanr"
)

cache <- FALSE
runModels <- FALSE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

# Fix
df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"] <- -1 * (df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"])
df[df$Illusion_Type == "Ebbinghaus", "Illusion_Difference"] <- round(df[df$Illusion_Type == "Ebbinghaus", "Illusion_Difference"], 5)

# Transformation
df$Illusion_Difference_log <- log(1 + df$Illusion_Difference)
df$Illusion_Difference_sqrt <- sqrt(df$Illusion_Difference)
df$Illusion_Difference_cbrt <- round(df$Illusion_Difference**(1 / 3), 4)
df$Illusion_Strength_log <- sign(df$Illusion_Strength) * log(1 + abs(df$Illusion_Strength))
df$Illusion_Strength_sqrt <- sign(df$Illusion_Strength) * sqrt(abs(df$Illusion_Strength))
df$Illusion_Strength_cbrt <- sign(df$Illusion_Strength) * (abs(df$Illusion_Strength)**(1 / 3))

@@

df <- read.csv("../data/study2.csv") |>
  mutate(
    Date = as.Date(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
  )
```

@@

# Dear participant, thank you for participating in our study. Unfortunately, we didn't receive your data :( did something happen? Some technical issue? We would like to kindly ask you to return your participation so that we can open up more slots. Thank you in advance, and apologies for the inconvenience!

@@

outliers <- c(
  # Error rate of 48.8% Very short RT
  # Prolific Status: REJECTED (06/08)
  "5e66ed53de7896486f9a71f8_p8ckk",
  # 2nd block of responses very fast
  # Prolific Status: RETURN REQUESTED (07/08)
  "61443e47c248a375c899a0cf_9qz3u"
)

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- df |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=20, height=15)

@@

p1 <- temp |>
  estimate_density(at = c("Illusion_Type", "Block")) |>
  ggplot(aes(x = x, y = y)) +
  geom_line(aes(color = Illusion_Type, linetype = Block)) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(y = "Distribution", x = "Error Rate") +
  theme_modern()

@@

p1 <- estimate_density(df, select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |>
    filter(Error == 0) |>
    group_by(Participant) |>
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |>
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(df, select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype = Outlier)) +
  geom_vline(xintercept = c(125), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

p2 <- df |>
  group_by(Participant) |>
  summarize(Outlier = sum(Outlier) / n()) |>
  mutate(Participant = fct_reorder(Participant, Outlier)) |>
  ggplot(aes(x = Participant, y = Outlier)) +
  geom_bar(stat = "identity", aes(fill = Participant)) +
  scale_fill_material_d("rainbow", guide = "none") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
  see::theme_modern() +
  theme(axis.text.x = element_blank())

p1 | p2
```

@@

p6 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_metro_d()

p7 <- plot_waffle(dfsub, "Ethnicity") +
  scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0"))

@@

(p1 / p2 / p3) | (p4 / p5 / p6) | (p7 / p8 / p9)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Delboeuf")
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
best_models(data)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ logmod(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + logmod(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache}

data <- filter(df, Illusion_Type == "Delboeuf", Error == 0)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
# formula <- brms::bf(
#   RT ~ Illusion_Difference * Illusion_Strength +
#     (1 + (Illusion_Difference * Illusion_Strength) | Participant),
#   sigma ~ Illusion_Difference * Illusion_Strength +
#     (1 + (Illusion_Difference * Illusion_Strength) | Participant),
#   # ndt ~ Illusion_Difference * Illusion_Strength +
#   #   (1 | G | Participant),
#   family = "shifted_lognormal"
# )
# formula <- brms::bf(
#   RT ~ Illusion_Difference * Illusion_Strength +
#     (1 + (Illusion_Difference * Illusion_Strength) | Participant),
#   sigma ~ Illusion_Difference * Illusion_Strength +
#     (1 + (Illusion_Difference * Illusion_Strength) | Participant),
#   # beta ~ Illusion_Difference * Illusion_Strength +
#   #   (1 + (Illusion_Difference * Illusion_Strength) | Participant),
#   family = "exgaussian"
# )

formula <- brms::bf(
  RT ~ logmod(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant),
  sigma ~ 1 + (1 | Participant),
  family = "exgaussian"
)
# prior = c(
#     prior(normal(6, 1.5), class = Intercept),
#     prior(normal(0, 1), class = sigma),
#     prior(normal(0, .01), class = b, coef = c_trial)
#   )

model_delboeuf_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2}
p_delboeuf <- plot_all(data, p_delboeuf_err, p_delboeuf_rt)
p_delboeuf
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=FALSE}
best_models(data)
```

@@

@@

model_ebbinghaus_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

model_rodframe_rt <- brms::brm(formula,
  data = data,
  refresh = 0
)

@@

#### Reliability

```{r message=FALSE, warning=FALSE, cache=cache}
random <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  # extract_random(model_delboeuf_rt, "Delboeuf"),
  extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  # extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    # !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong_"),
    !str_detect(Parameter, "Null_"))

random |>
  # group_by(Illusion_Type, Parameter) |> 
  # standardize(select="Value") |> 
  # ungroup() |> 
  # mutate(order = mean(Value)) |> 
  # ungroup() |> 
  # mutate(Participant = fct_reorder(Participant, order)) |> 
  ggplot(aes(y = Participant, x = Value)) +
  ggdist::stat_slabinterval(aes(fill = Illusion_Type, color=Illusion_Type), alpha=0.5) +
  # coord_cartesian(xlim=c(-4, 4)) +
  facet_wrap(~Parameter, scales = "free_x")

@@

<!-- #### Approximation -->

>>>>

```{r, echo = FALSE, warning=FALSE, message=FALSE}
options(
  digits = 3,
  mc.cores = 4,
  brms.algorithm = "sampling",
  brms.backend = "cmdstanr"
)

cache <- TRUE
runModels <- TRUE
bestModels <- TRUE
fig.width <- see::golden_ratio(7)
fig.height <- 7

@@

# Fix
df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"] <- -1 * (df[df$Illusion_Type == "Rod-Frame" & df$Date == "05/08/2022", "Illusion_Strength"])

@@

df <- read.csv("../data/study2.csv") |>
  mutate(
    Date = lubridate::dmy(Date),
    Participant = fct_reorder(Participant, Date),
    Screen_Refresh = as.character(Screen_Refresh),
    Illusion_Side = as.factor(Illusion_Side),
    # Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Null", "Congruent"),
    Illusion_Effect = fct_relevel(as.factor(Illusion_Effect), "Incongruent", "Congruent"),
    Block = as.factor(Block),
    Education = fct_relevel(Education, "Doctorate", "Master", "Bachelor", "High School", "Other")
  )

# Fix precision
for(ill in unique(df$Illusion_Type)) {
  data <- df[df$Illusion_Type == ill, ] 
  i <- 10
  while (length(sort(unique(signif(data$Illusion_Difference, i)))) != 8) {
    i <- i - 1
  }
  df[df$Illusion_Type == ill, "Illusion_Difference"] <- signif(df[df$Illusion_Type == ill, "Illusion_Difference"], i)
  if (i != 10) {
    message(ill, ": Illusion_Difference values != 8. Rounded to ", i, ".")
  }
}

# Transformation
df <- df |> 
  mutate(    
    Illusion_Difference_log = log(1 + Illusion_Difference),
    Illusion_Difference_sqrt = sqrt(Illusion_Difference),
    Illusion_Difference_cbrt = Illusion_Difference**(1 / 3),
    Illusion_Strength_log = sign(Illusion_Strength) * log(1 + abs(Illusion_Strength)),
    Illusion_Strength_sqrt = sign(Illusion_Strength) * sqrt(abs(Illusion_Strength)),
    Illusion_Strength_cbrt = sign(Illusion_Strength) * (abs(Illusion_Strength)**(1 / 3))
    )
```

@@

# Dear participant, thank you for participating in our studfy. Unfortunately, we didn't receive your data :( did something happen? Some technical issue? We would like to kindly ask you to return your participation so that we can open up more slots. Thank you in advance, and apologies for the inconvenience!

@@

outliers <- c(
  # Error rate of 48.8% Very short RT
  # Prolific Status: REJECTED (06/08)
  "5e66ed53de7896486f9a71f8_p8ckk",
  # 2nd block of responses very fast
  # Prolific Status: REJECTED (15/08)
  "61443e47c248a375c899a0cf_9qz3u"
)

@@

```{r message=FALSE, warning=FALSE, fig.width=20, fig.height=20}
# RT distribution
p <- df |> 
  # filter(Date > "2022-08-12") |> 
  filter(RT < 10000) |> 
  estimate_density(select = "RT", at = c("Participant", "Block")) |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  mutate(Participant = factor(Participant, levels=levels(df$Participant))) |> 
  mutate(color = ifelse(Participant %in% outliers, "red", ifelse(Participant %in% partial_outliers, "orange", "blue"))) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = color, group = interaction(Participant, Block), linetype = Block)) +
  geom_vline(xintercept = 125, linetype = "dashed", color = "red") +
  scale_color_manual(values = c("red" = "#F44336", "orange" = "#FF9800", "blue" = "blue"), guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  coord_cartesian(xlim = c(0, 3000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  facet_wrap(~Participant) +
  labs(y = "", x = "Reaction Time (ms)")
# p
# ggsave("figures/outliers.png", p, width=20, height=15)

@@

p1 <- temp |>
  estimate_density(at = c("Illusion_Type", "Block"), method="KernSmooth") |>
  ggplot(aes(x = x, y = y)) +
  geom_line(aes(color = Illusion_Type, linetype = Block)) +
  geom_vline(xintercept = 0.5, linetype = "dashed") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(y = "Distribution", x = "Error Rate") +
  theme_modern()

@@

p1 <- estimate_density(df, select = "RT", at = "Participant") |>
  group_by(Participant) |>
  normalize(select = "y") |>
  ungroup() |>
  merge(df |>
    filter(Error == 0) |>
    group_by(Participant) |>
    summarize(Outlier = mean(RT) + 4 * sd(RT))) |>
  mutate(Outlier = ifelse(x >= Outlier, TRUE, FALSE)) |>
  ggplot(aes(x = x, y = y)) +
  geom_area(data = normalize(estimate_density(filter(df, RT < 10000), select = "RT"), select = "y"), alpha = 0.2) +
  geom_line(aes(color = Participant, linetype = Outlier), alpha=0.2) +
  geom_vline(xintercept = c(125), linetype = "dashed", color = "red") +
  scale_color_material_d("rainbow", guide = "none") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  guides(linetype = "none") +
  coord_cartesian(xlim = c(0, 4000)) +
  theme_modern() +
  theme(axis.text.y = element_blank()) +
  labs(y = "", x = "Reaction Time (ms)")

p2 <- df |>
  group_by(Participant) |>
  summarize(Outlier = sum(Outlier) / n()) |>
  mutate(Participant = fct_reorder(Participant, Outlier)) |>
  ggplot(aes(x = Participant, y = Outlier)) +
  geom_bar(stat = "identity", aes(fill = Participant)) +
  scale_fill_material_d("rainbow", guide = "none") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0), labels = scales::percent) +
  see::theme_modern() +
  theme(axis.text.x = element_blank()) +
  labs(y = "Percentage of outlier trials")

p1 / p2
```

@@

p6 <- plot_waffle(dfsub, "Nationality") +
  scale_fill_manual(values = c("South American" = "#FF5722", "Middle Eastern" = "#FF9800", "Western" = "#2196F3", "African" = "#4CAF50", "South African" = "#009688"))

p7 <- plot_waffle(dfsub, "Ethnicity") +
  scale_fill_manual(values = c("Latino" = "#FF5722", "Asian" = "#FF9800", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Jewish" = "#9C27B0", "Mixed" = "#795548"))

@@

(p1 / p2 / p3) | (p4 / p5 / p9) | (p6 / p7 / p8)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Delboeuf")

# mm <- model.matrix(Error ~ abs(Illusion_Strength) * Illusion_Effect, data=data)
# head(as.data.frame(mm))
```

```{r message=FALSE, warning=FALSE, cache=cache, eval=bestModels}
best_models(data)
```

@@

@@

```{r message=FALSE, warning=FALSE, cache=cache}
data <- filter(df, Illusion_Type == "Delboeuf", Error == 0)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

# brms::get_prior(formula, data = data)
# plot(seq(-5, 5, length.out=100), brms::dstudent_t(seq(-5, 5, length.out=100), df = 3, 0.1, 0.5))
priors <- c(
  # Intercept
  prior("student_t(3, 0, 0.1)", class = "Intercept"),
  prior("student_t(3, 0.35, 0.1)", class = "sd", coef="Intercept", group="Participant"),
  # Default parameters
  prior("student_t(3, 0, 3)", class = "b"),
  prior("student_t(3, 0.35, 0.5)", class = "sd", group="Participant")

  # prior("student_t(3, 0, 1)", class="Intercept", dpar = "sigma"),
  # prior("student_t(3, 0.1, 1)", class="sd", dpar = "sigma")

  # prior("student_t(3, 0.1, 0.5)", class = "ndt")
  ) |> 
  brms::validate_prior(formula, data = data)

# bayestestR::model_to_priors(model_delboeuf_rt, scale_multiply=3)

model_delboeuf_rt <- brms::brm(formula,
  data = data,
  refresh = 50,
  init=0
)

@@

```{r message=FALSE, warning=FALSE, cache=cache, fig.height=fig.height*2, eval=FALSE}
p_delboeuf <- plot_all(data, p_delboeuf_err, p_delboeuf_rt)
p_delboeuf
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=bestModels}
best_models(data)
```

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  Error ~ sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  family = "bernoulli"
)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect +
    (1 + sqrt(Illusion_Difference) * logmod(abs(Illusion_Strength)) * Illusion_Effect | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

model_ebbinghaus_rt <- brms::brm(formula,
  data = data,
  refresh = 0,
  init = 0
)

@@

```{r message=FALSE, warning=FALSE, cache=cache, eval=runModels}
formula <- brms::bf(
  RT ~ sqrt(Illusion_Difference) * sqrt(abs(Illusion_Strength)) * Illusion_Effect +
    (1 | Participant),
  sigma ~ 1 + (1 | Participant),
  beta ~ 1 + (1 | Participant),
  family = "exgaussian"
)

model_rodframe_rt <- brms::brm(formula,
  data = data,
  refresh = 0,
  init = 0
)

@@

### Reliability

```{r message=FALSE, warning=FALSE, cache=cache}
random <- rbind(
  extract_random(model_delboeuf_err, "Delboeuf"),
  extract_random(model_delboeuf_rt, "Delboeuf")
  # extract_random(model_ebbinghaus_err, "Ebbinghaus"),
  # extract_random(model_ebbinghaus_rt, "Ebbinghaus"),
  # extract_random(model_rodframe_err, "Rod-Frame"),
  # extract_random(model_rodframe_rt, "Rod-Frame"),
  # extract_random(model_verticalhorizontal_err, "Vertical-Horizontal"),
  # extract_random(model_verticalhorizontal_rt, "Vertical-Horizontal"),
  # extract_random(model_zollner_err, "Zöllner"),
  # extract_random(model_zollner_rt, "Zöllner"),
  # extract_random(model_white_err, "White"),
  # extract_random(model_white_rt, "White"),
  # extract_random(model_mullerlyer_err, "Müller-Lyer"),
  # extract_random(model_mullerlyer_rt, "Müller-Lyer"),
  # extract_random(model_ponzo_err, "Ponzo"),
  # extract_random(model_ponzo_rt, "Ponzo"),
  # extract_random(model_poggendorff_err, "Poggendorff"),
  # extract_random(model_poggendorff_rt, "Poggendorff"),
  # extract_random(model_contrast_err, "Contrast")
  # extract_random(model_contrast_rt, "Contrast")
) |> 
  filter(
    # !str_detect(Parameter, "Intercept_"),
    !str_detect(Parameter, "Cong_"),
    !str_detect(Parameter, "Null_"))

random |>
  # group_by(Illusion_Type, Parameter) |> 
  # standardize(select="Value") |> 
  # ungroup() |> 
  # mutate(order = mean(Value)) |> 
  # ungroup() |> 
  # mutate(Participant = fct_reorder(Participant, order)) |> 
  ggplot(aes(y = Participant, x = Value)) +
  # ggdist::stat_slabinterval(aes(fill = Illusion_Type, color=Illusion_Type), alpha=0.5) +
  ggdist::stat_pointinterval(aes(fill = Illusion_Type, color=Illusion_Type), alpha=0.5) +
  # coord_cartesian(xlim=c(-4, 4)) +
  facet_wrap(~Parameter, scales = "free_x") +
  theme(axis.text.y = element_blank())

@@

### Relationship with empirical descriptors

```{r message=FALSE, warning=FALSE, cache=cache}
empirical <- df |>
  group_by(Participant, Illusion_Type) |>
  summarize(
    # n = n(),
    Error = sum(Error, na.rm=TRUE) / n(),
    RT_Mean = mean(RT, na.rm=TRUE),
    RT_SD = sd(RT, na.rm=TRUE),
  ) |>
  ungroup()

r <- correlation::correlation(
  data = random |> 
    arrange(Participant) |> 
    data_select(select="Delboeuf", regex=TRUE),
  data2 = empirical |>
    filter(Illusion_Type %in% c("Delboeuf")) |> 
    pivot_wider(names_from = c("Illusion_Type"), values_from = c("Error", "RT_Mean", "RT_SD")) |> 
    arrange(Participant)
  )

plot(summary(r))
```
<!-- ### Approximation -->
